PAMELA: an annotation-based Java Modeling Framework

### 2021-02-09 6-Experimentations.tex
add few references

Model Federation is an approach that provides the means to integrate multiple models conforming to different paradigms, and giving to each stakeholder a specific view adapted to its needs. Model federation approach is developed as a possible response to SIMF RFP (Semantic Information Modeling for Federation) by OMG (Object Modeling Group). This RFP (Request For Proposal) requests submissions for a standard addressing, ”federation of information across different representations, levels of abstraction, communities, organizations, viewpoints, and authorities”. Thus model federation allows the integration of heterogeneous models to develop new cross-concern viewpoints/models or to synchronize the models used for designing a system.

@@

The main results of the project are a requirements modeling multi-views language, its associated design process and the development of an opensource platform called Formod\cite{FormodWebSite}, built using Openflexo infrastructure and PAMELA framework. The requirements modeling language is based on KAOS for goal modeling and SysML for the structural part of a system. The associated domain modeling language, used to describe system domain knowledge, extends the two ontology languages OWL and PLIB. The graphical notations are then translated into Event-B, a formal specification method supported by verification tools.

>>>>

Model Federation~\cite{Golra2016} is an approach that provides the means to
integrate multiple models conforming to different paradigms, and giving to each
stakeholder a specific view adapted to its needs. Model federation approach is
developed as a possible response to SIMF RFP (Semantic Information Modeling for
Federation)i~\cite{simf-rfp} by OMG (Object Modeling Group). This RFP (Request For Proposal)
requests submissions for a standard addressing, ”federation of information
across different representations, levels of abstraction, communities,
organizations, viewpoints, and authorities”. Thus model federation allows the
integration of heterogeneous models to develop new cross-concern
viewpoints/models or to synchronize the models used for designing a system.

@@

The main results of the project are a requirements modeling multi-views
language, its associated design process and the development of an opensource
platform called Formod\cite{FormodWebSite}, built using Openflexo
infrastructure and PAMELA framework. \todo{Say how and where PAMELA was used}
The requirements modeling language is based on KAOS~\cite{kaos} for goal
modeling and SysML for the structural part of a system. The associated domain
modeling language, used to describe system domain knowledge, extends the two
ontology languages OWL~\cite{owl} and PLIB~\cite{plib}. The graphical notations
are then translated into Event-B~\cite{eventb}, a formal specification method supported by verification tools.

\todo{Remark that it is industry ready}
